SSA based global code motion of identical computations

### 2017-04-16 acmart-pacmpl-template.tex
downward safety

\subsection{Finding candidates to move}
The first step is to find a set of instructions that perform identical
computations: this is performed by a linear scan of all instructions of the
program and classifying all instructions by their value given by \GVN{}. We
could computed available and anticipable sets as computed by GCC's code-hoisting
but that would be a lot of data structures to maintain at each basic block
level. For GCC it makes sense because their code-hoisting is integrated with
GVN-PRE which already has those data structures available.

@@

@@

For each value number VN with 2 or more instructions:
  sort the instructions according to DFSIn numbers
  if first two I1, I2 are hoistable:
    if they are anticipable at hoist-point:
      if they are profitable to be hoisted at hoist-point:
        proceed to check hoistability of subsequent instruction with same VN
      else
        proceed to check if I2 and I3 (if available) is hoistable

>>>>

\subsection{Finding candidates to move}
The first step is to find a set of instructions that perform identical
computations: this is performed by a linear scan of all instructions of the
program and classifying all instructions by their value given by \GVN{}. We
could compute available and anticipable sets as computed by GCC's code-hoisting
but that would be a lot of data structures to maintain at each basic block
level. For GCC it makes sense because their code-hoisting is integrated with
GVN-PRE which already has those data structures available.

@@

computing barriers:

\begin{verbatim}
computing downward-safety of hoistable instructions at hoist-point
Worklist = list of all basic blocks of hoistable instructions
for each basic block B in the dominator tree starting at hoist-point:
  if Worklist is empty
    return false // Path exists! not downward safe
  if B is in Worklist:
    remove B from worklist
    remove subtree with root at B // Available at B => downward safe from B
  if B is a leaf basic block:
    return false  // Path exists! not downward safe
  if B dominates hoist-point:
    return false  // Back edge

@@

For each value number VN with 2 or more instructions:
  sort the instructions according to DFSIn numbers
  if first two I1, I2 are hoistable:
    if they are downward-safe at hoist-point:
      if they are profitable to be hoisted at hoist-point:
        proceed to check hoistability of subsequent instruction with same VN
      else
        proceed to check if I2 and I3 (if available) is hoistable
